Perceptual symbol grounding in \\Holographic memories

### 2016-11-11 papers/hrr-paper/paper.tex
Replaced the cover photo.

	\begin{figure}
		\center
		\includegraphics[width=0.9\columnwidth]{img/cover_photo.png}
		\caption{In-memory representation of top-down attention shift for visual scene short-term  memory}
	\end{figure}

>>>>

	\begin{figure}
		\center
		\includegraphics[width=0.9\columnwidth]{img/probe_for_pen_w_img.png}
		\caption{In-memory representation of top-down attention shift for visual scene short-term memory. Result shows attention distribution for a symbol "pen".}
	\end{figure}
